Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data

### 2024-11-04 paper/paper.qmd
update paper

In this study, we utilized several R packages to enhance our data
manipulation, modeling, and visualization capabilities. The tidyverse
package offered a detailed set of tools for data wrangling and
analysis, improving workflow efficiency [@thereferencecanbewhatever].
The here package aided in managing file paths, allowing for easy access
to our data files [@citehere]. We relied on janitor to perform data
cleaning, as it provides functionalities to identify and rectify quality
issues within the dataset [@citejanitor]. For handling date-related
operations, the lubridate package proved invaluable, simplifying the
manipulation of time variables [@citelubridate]. Arrow supported
efficient data input and output in a performance-oriented format,
essential for managing larger datasets [@citearrow]. We use ggplot2 [@citeggplot2] to visualize the analysis of data. In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks. The modelsummary package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary]. RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer]. The future package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture]. Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2]. caret facilitated model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret]. Our coding practices and file organization were informed by the structure outlined
in @tellingstories.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Harris Kamala leads Donald Trump an average 2% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
#| fig-subcap: ["Unweighted","Weighted"]
#| layout-ncol: 1
#| label: fig-support-trend
# Plotting with the filtered data
plan(multisession)
##unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted),size = 0.2)+
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Linear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
           label = "46.5%", color = "red", hjust = -0.2, size = 2)

##weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.2)+
  labs(x = "End Date of the Poll",
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nLinear Regression Model: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
           label = "46.5%", color = "red", hjust = -0.2, size = 2)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-subcap: ["Unweighted","Weighted"]
#| layout-ncol: 1
#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, Michigan, and Wisconsin by Model Prediction"
#| label: fig-support-state
## unweighted
plan(multisession)
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
late<-combined_predictions_filtered[which.max(combined_predictions_filtered$end_date), ]
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate))+
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+
  facet_wrap(~ state,ncol = 4) +
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1, size =6),
        legend.box = "vertical",
        strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.5)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight\nCandidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1,size=6),
        legend.box = "vertical",
        strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

ggplot(combined_data_total, aes(x = end_date, y = pct)) +
  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_unweighted), color = "blue", size = 1) +
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
  labs(
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    color = "Candidate",
    fill = "Top 5 Pollster",
    caption = "Candidate Support Percentage = national_poll + pollster + population + state"
  )+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(brewer.pal(10, "Set1"), top_pollsters))) + 
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1,size=8),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_weighted), color = "blue", size = 1) +
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_weighted), color = "red", size = 1)+
  labs(
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    size = "Weight",
    fill = "Top 5 Pollster",
    caption = "Weights: recency_weight * sample_size_weight \nCandidate Support Percentage = national_poll + pollster + population + state"
  )+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(brewer.pal(10, "Set1"), top_pollsters))) +
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1,size=8),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

@@

RMSE (Root Mean Square Error): Measures the average magnitude of
prediction errors (lower is better).

Harris Model: RMSE of 2.43, indicating an average prediction error of
around 2.43 percentage points.\
Trump Model: RMSE of 2.57, showing a slightly average prediction error on
average.\

@@

MAE (Mean Absolute Error): Shows the average absolute difference between
observed and predicted values (lower is better).\
Harris Model: MAE of 1.6, meaning that, on average, the predictions are
off by 1.62 percentage points.\
Trump Model: MAE of 1.62, indicating slightly higher precise predictions
compared to the Harris model.\

Interpretation Summary Predictive Accuracy: The Harris model has
slightly better predictive accuracy than the Trump model, as reflected
by its lower RMSE and MAE values.\
Model Fit: Harris' model explains roughly 63% of the variance in their
respective datasets. Trump's models explain roughly 66% of the variance
in their respective datasets. This suggests that other factors not
included in the model may play a significant role in explaining the
remaining variance.\
This summary indicates the models are moderately predictive, with room
for improvement in accuracy and fit, potentially by adding more
predictors or adjusting model specifications.\

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Harris"
#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
#| layout-ncol: 2

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-dia
#| fig-cap: "Diagnostics of model using residual vs fitted plot and norm Q-Q plot\n-Support for Trump"
#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
#| layout-ncol: 2

@@

This survey is for academic research in Statistics. It consists of 26
carefully designed questions and should take approximately 12-15 minutes
to complete.

@@

4.  **How favorable are you towards the following candidates?**

    |               | Very unfavorable | Unfavorable | Moderate | Favorable | Very favorable |
    |------------|------------|------------|------------|------------|------------|
    | Kamala Harris |                  |             |          |           |                |
    | Donald Trump  |                  |             |          |           |                |

5.  **How likely are you going to vote in the 2024 election?** (1 =
    Definitely not to vote, 10 = Definitely will vote)

@@

6.  **How do you plan to cast your vote?**

@@

7.  **Did you vote in the 2020 U.S. presidential election?**

@@

8.  **If you voted in 2020, who did you vote for?**

@@

9.  **Imagine the following candidates: Candidate A favors cutting taxes
    but has a weak stance on climate change, and Candidate B focuses on
    healthcare but supports increased military spending. Who would you
    vote for?**

@@

10. **What do you think is the most important issue facing the United
    States?** \[Select at most 3\]

@@

11. **Select option 3 from the list below:**

@@

12. **Which social media platforms do you use to get political news?**
    (Select all that apply)

>>>>

In this study, we utilized several R packages to enhance our data
manipulation, modeling, and visualization capabilities. The `tidyverse`
package offered a detailed set of tools for data wrangling and
analysis, improving workflow efficiency [@thereferencecanbewhatever].
The `here` package aided in managing file paths, improving the reproducible workflow of our study [@citehere].We use `testthat` to verify dataset variables, ensuring they are correctly formatted and contain expected values for analysis [@citetestthat]. We relied on `janitor` to perform data
cleaning, as it provides functionalities to identify and rectify quality
issues within the dataset [@citejanitor]. For handling date-related
operations, the `lubridate` package help simplifying the
manipulation of time variables [@citelubridate]. `arrow` supported
efficient data input and output in a parquet format,
essential for managing larger datasets [@citearrow]. We use `ggplot2` [@citeggplot2] to visualize the analysis of data. In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks. The `modelsummary` package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary]. `RColorBrewer` provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer]. The `future` package supported parallel processing, optimizing the runtime of intensive computations, which is especially beneficial in model training [@citefuture]. Finally,for validation of model using K-Fold cross validation, we utilized the `boot` package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2] and `caret` to facilitate model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret]. Our coding practices and file organization were informed by the structure outlined
in @tellingstories.

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-cap: "Harris Kamala leads Donald Trump an average 1% in Predicted Support in the 2024 US Election (From August 1, 2024, to November 2, 2024)"
#| fig-subcap: ["Unweighted","Weighted"]
#| layout-ncol: 1
#| label: fig-support-trend
# Plotting with the filtered data
plan(multisession)
##unweighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate)) +
  geom_point(alpha = 0.1)+ 
  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted),size = 0.2)+
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",caption = 
                   "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
           label = "46.5%", color = "red", hjust = -0.2, size = 2)

##weighted
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_smooth(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), method = "lm",size = 1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.2)+
  labs(x = "End Date of the Poll",
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red"))  +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 45, hjust = 1),strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) +
  annotate("text", x = max(combined_predictions_filtered$end_date) -0.5, y = 48, 
           label = "47.5%", color = "blue", hjust = -0.2, size = 2) +  # Adjust size here
  annotate("text", x = max(combined_predictions_filtered$end_date) - 0.5, y = 46, 
           label = "46.5%", color = "red", hjust = -0.2, size = 2)
```

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| fig-subcap: ["Unweighted","Weighted"]
#| layout-ncol: 1
#| fig-cap: "Harris is likely to lead Trump in Pennsylvania, Michigan, and Wisconsin by Model Prediction"
#| label: fig-support-state
## unweighted
plan(multisession)
selected_states <- c("Arizona", "Georgia", "Michigan", "Nevada", "North Carolina", "Pennsylvania", "Wisconsin")
combined_data_total<-combined_data_total|>filter(state %in% selected_states)
combined_predictions_filtered<-combined_predictions_filtered|>filter(state %in% selected_states)
late<-combined_predictions_filtered[which.max(combined_predictions_filtered$end_date), ]
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate))+
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_unweighted), size = 0.5)+
  facet_wrap(~ state,ncol = 4) +
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1, size =6),
        legend.box = "vertical",
        strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

## weighetd
ggplot(combined_data_total,aes(x = end_date,y=pct, colour = candidate,size = combined_weight)) +
  geom_point(alpha = 0.1)+ 
  geom_line(data = combined_predictions_filtered,aes(x=end_date,y = predicted_weighted), size = 0.5)+ # Smoothed trend line
  facet_wrap(~ state,ncol = 4) +
  labs(
       x = "End Date of the Poll",  # Change x-axis label to End Date
       y = "Predicted Support (%)",
       color = "Candidate",
       size="Weight",
       caption = "Weights: recency_weight * sample_size_weight\nModel: Candidate Support Percentage = national_poll + pollster + population + state") +
  scale_color_manual(values = c("Kamala Harris" = "blue", "Donald Trump" = "red")) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, hjust = 1,size=6),
        legend.box = "vertical",
        strip.background = element_rect(colour = "black", fill = "white")) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date)) 
```

@@

ggplot(combined_data_total, aes(x = end_date, y = pct)) +
  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_unweighted), color = "blue", size = 1) +
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_unweighted), color = "red", size = 1) +
  labs(
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    color = "Candidate",
    fill = "Top 5 Pollster",
    caption = "Model: Candidate Support Percentage = national_poll + pollster + population + state"
  )+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(brewer.pal(10, "Set1"), top_pollsters))) + 
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1,size=8),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

ggplot(combined_data_total, aes(x = end_date, y = pct, size = combined_weight)) +
  geom_point(aes(fill = pollster_group), alpha = 0.7, shape = 21) + 
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Kamala Harris"), 
            aes(x = end_date, y = predicted_weighted), color = "blue", size = 1) +
  geom_smooth(data = combined_predictions_filtered %>% filter(candidate == "Donald Trump"), 
            aes(x = end_date, y = predicted_weighted), color = "red", size = 1)+
  labs(
    x = "End Date of the Poll",
    y = "Predicted Support (%)",
    size = "Weight",
    fill = "Top 5 Pollster",
    caption = "Weights: recency_weight * sample_size_weight \nModel: Candidate Support Percentage = national_poll + pollster + population + state"
  )+ # Smoothed trend line
  facet_wrap(~ candidate,ncol = 2) +
  scale_fill_manual(values = c(setNames(rep("grey", length(unique(combined_data_total$pollster_group))), "Other"),
                               setNames(brewer.pal(10, "Set1"), top_pollsters))) +
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.box = "vertical",  # Place legends in a horizontal row
    legend.title.align = 0.5,   # Center-align legend titles for better appearance
    axis.text.x = element_text(angle = 45, hjust = 1,size=8),
    strip.background = element_rect(colour = "black", fill = "white")
  ) +
  guides(
    size = guide_legend(order = 1, title.position = "top", label.position = "left"),
    fill = guide_legend(order = 2)
  ) +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 week", limits = c(recent_date_cutoff, max_end_date))

@@

RMSE (Root Mean Square Error): Measures the average magnitude of
prediction errors (lower is better).\
Harris Model: RMSE of 2.43, indicating an average prediction error of
around 2.43 percentage points.\
Trump Model: RMSE of 2.57, showing a slightly average prediction error on
average.

@@

MAE (Mean Absolute Error): Shows the average absolute difference between
observed and predicted values (lower is better).\
Harris Model: MAE of 1.6, meaning that, on average, the predictions are
off by 1.62 percentage points.\
Trump Model: MAE of 1.62, indicating slightly higher precise predictions
compared to the Harris model.

In summary, the Harris model has slightly better predictive accuracy than the Trump model, as reflected
by its lower RMSE and MAE values. Harris' model explains roughly 63% of the variance in their
respective datasets, while Trump's models explain roughly 66% of the variance
in their respective datasets. This suggests that other factors not
included in the model may play a significant role in explaining the
remaining variance. This K-Fold Cross-Validation indicates the models are moderately predictive, with room for improvement in accuracy and fit, potentially by adding more
predictors or adjusting model specifications.

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Diagnostics of Support for Harris model using residual vs fitted plot and norm Q-Q plot"
#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
#| layout-ncol: 2

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-dia
#| fig-cap: "Diagnostics of Support for Trump model using residual vs fitted plot and norm Q-Q plot"
#| fig-subcap: ["Residual Plot for Unweighted Model", "Q-Q Plot for Unweighted Model", "Residual Plot for Weighted Model", "Q-Q Plot for Weighted Model"]
#| layout-ncol: 2

@@

This survey is for academic research in Statistics. It consists of 26
carefully designed questions and should take approximately 10-15 minutes
to complete.

@@

4.  **How favorable are you towards the Kamala Harris?** (1 = 
    Very Unfavorable, 5 = Very Favorable)

    -   1
    -   2
    -   3
    -   4
    -   5

5. **How favorable are you towards the Donald Trump?** (1 = 
    Very Unfavorable, 5 = Very Favorable)

    -   1
    -   2
    -   3
    -   4
    -   5

6.  **How likely are you going to vote in the 2024 election?** (1 =
    Definitely not to vote, 10 = Definitely will vote)

@@

7.  **How do you plan to cast your vote?**

@@

8.  **Did you vote in the 2020 U.S. presidential election?**

@@

9.  **If you voted in 2020, who did you vote for?**

@@

10.  **Imagine the following candidates: Candidate A favors cutting taxes
    but has a weak stance on climate change, and Candidate B focuses on
    healthcare but supports increased military spending. Who would you
    vote for?**

@@

11. **What do you think is the most important issue facing the United
    States?** \[Select at most 3\]

@@

12. **Select option 3 from the list below:**

@@

13. **Which social media platforms do you use to get political news?**
    (Select all that apply)
